Phenology and Mycorrhizae Manuscript

### 2023-02-01 manuscriptCode_phenologyAndMycorrhizae.Rmd
updated

#Download Relative Humidity
```{r}
dataName="NEON_RH"
NEON_ID='DP1.00098.001'
if(!file.exists(paste0(dataPath,"/",dataName))){
  dir.create(paste0(dataPath,"/",dataName))
}
# selectColumns <- c('verticalPosition','PARMean','PARMinimum','PARMaximum','PARVariance','PARFinalQF')
# inFileName <- "PARPAR_30min.csv"
# varName <- "PARMean"

>>>>

#Download Relative Humidity
```{r}
dataName="NEON_relativeHumidity"
NEON_ID='DP1.00098.001'
if(!file.exists(paste0(dataPath,"/",dataName))){
  dir.create(paste0(dataPath,"/",dataName))
}
selectColumns <- c('verticalPosition','RHMean','RHMinimum','RHMaximum','RHVariance','dewTempMean',
                   'RHFinalQF','dewTempFinalQF')
inFileName <- "RH_30min.csv"
varName <- "RHMean"

# funType=mean
# funName="mean"
# calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funType,funName=funName)
# 
# funType=min
# funName="min"
# calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funType,funName=funName)
# 
# funType=max
# funName="max"
# calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funType,funName=funName)

#Download Windspeed
```{r}
dataName="NEON_Windspeed"
NEON_ID='DP1.00001.001'
if(!file.exists(paste0(dataPath,"/",dataName))){
  dir.create(paste0(dataPath,"/",dataName))
}
selectColumns <- c('verticalPosition','windSpeedMean','windSpeedMinimum','windSpeedMaximum','windSpeedFinalQF')
inFileName <- "2DWSD_30min.csv"
varName <- "windSpeedMean"
